Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.

### 2015-05-15 papers/MbhMsph/mm.tex
fri

\shorttitle{M-M paper}
\shortauthors{Savorgnan et al.}

@@

\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}

@@

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulges, disks, bars, spiral arms, rings, haloes, nuclei, cores, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked to be consistent with the galaxy kinematics.
Here we present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they grow. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$. {\bf 241 words}

@@

\keywords{\bf keywords}

@@

i.e. a linear and a quadratic correlation at the high- and low-mass end, respectively.

@@

The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations that involve 

@@

{\bf This paper is structured as follows... }

@@

whereas two galaxies classified as S0/Sp or another two classified as mergers are included in neither the early- nor the late-type bin.\\

@@

Galaxies with velocity dispersions between these bands had high-resolution images available. \\

@@

\subsection{Black hole mass -- galaxy luminosity}
The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
Our $M_{\rm BH} - L_{\rm sph}$ relation for 66 galaxies, irrespective of their morphological type, 
has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. \\
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing the error associated with $L_{\rm gal}$ 
(we originally assumed $0.25\rm~mag$).
The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
when assuming an error of $L_{\rm gal}$ $\geq 0.7\rm~mag$, 
which would be oddly larger than the typical error of $L_{\rm sph}$ used here 
and also significantly larger than the errors of $L_{\rm gal}$ commonly assumed in the literature.
Hence, we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%We decided to vary only the errors associated to $L_{\rm gal}$ 
%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
%that takes into account the systematic errors related to the galaxy decomposition process. 
%We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
%have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
%Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
%and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
%we conclude that our determination of the intrinsic scatter is reliable, 
%and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
%than performing accurate galaxy decompositions to obtain bulge luminosities. 
%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
but not for all (early+late) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

@@

This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.

@@

The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter than in GS13. 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ relation -- 
which is expected for consistency with other scaling relations 
(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
We now test a new hypothesis, where the change in slope is ascribed to the different formation mechanisms of early- and late-type galaxies. 
If this hypothesis is correct, 
the spheroids of early-type galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
whereas the spheroids of late-type galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.

@@

and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$ respectively, 
in excellent agreement with the theoretical expectations of our hypothesis. \\
%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans. 
More data would be welcome to better constrain the slope of this \emph{blue sequence}.
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $= 2.28^{+1.67}_{-1.01}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.

Using data from \cite{jiang2011a}, 
\cite{grahamscott2015} collected a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the tentative \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated analysis. \\

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type.
The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
a near-linear relation consistent with a dry-merging formation scenario.
The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
(see Graham et al. 2015, \emph{in preparation}).}
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\acknowledgments
GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz for useful discussion. \\
% referee thank you!!
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at {\url https://github.com/rsnemmen/BCES}.

>>>>

\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
\shortauthors{Savorgnan et al.}

@@

\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}

@@

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulges, disks, bars, spiral arms, rings, haloes, nuclei, cores, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked to be consistent with the galaxy kinematics.
Here we present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{late sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they grow. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$. {\bf 241 words}

@@

\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}

@@

i.e. a linear and a super-quadratic correlation at the high- and low-mass end, respectively.

@@

The $M_{\rm BH} - L_{\rm sph}$ relation for early-type (elliptical + lenticular) galaxies can be predicted from other two correlations that involve 

@@

%{\bf This paper is structured as follows... }

@@

whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.\\

@@

Galaxies with velocity dispersions between these bands had high-resolution images available.

@@

\subsection{Black hole mass -- galaxy luminosity}
The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
Our $M_{\rm BH} - L_{\rm sph}$ relation for 66 galaxies, irrespective of their morphological type, 
has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. \\
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing such uncertainties  
(we originally assumed $0.25\rm~mag$).
The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
when assuming for $L_{\rm gal}$ an uncertainty larger than $0.7\rm~mag$, 
which would be significantly larger than the values commonly assumed in the literature, 
and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
Hence, we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%We decided to vary only the errors associated to $L_{\rm gal}$ 
%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
%that takes into account the systematic errors related to the galaxy decomposition process. 
%We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
%have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
%Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
%and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
%we conclude that our determination of the intrinsic scatter is reliable, 
%and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
%than performing accurate galaxy decompositions to obtain bulge luminosities. 
%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
%%%We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
but not for all (early+late) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

@@

This results in our bulge magnitudes being on average $\sim$$0.7\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.

@@

The magnitudes that we obtained for such spheroids are on average $\sim$$0.5\rm~mag$ brighter than in GS13. 

@@

We have seen that the slope that we obtained for S\'ersic spheroids ($1.53 \pm 0.20$) is not consistent with the $2.5$ 
expected from $M_{\rm BH} \propto \sigma^5$ and $L_{\rm sph} \propto \sigma^2$, 
and also that S\'ersic and core-S\'ersic spheroids do not define two distinct $M_{\rm BH} - L_{\rm sph}$ sequences. 
We now investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ diagram for early- and late-type galaxies.

@@

and thus, taken together, they define a single \emph{early sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
We then fit the bulges of early-type galaxies with a single log-linear regression, 
and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$. 
We did not find any convincing evidence for the change in slope expected for consistency 
with the $M_{\rm BH} - \sigma$ and $L_{\rm sph} - \sigma$ correlations. 
Because the change in slope should occur at $M_{\rm BH} > 10^{8 \pm 1}\rm~M_\odot$, 
but all the early-type galaxies in our sample have $M_{\rm BH} \gtrsim 10^7\rm~M_\odot$, 
one possible explanation is that we are still not probing enough low black hole masses for this subsample.
An alternative possibility is that there is no sharp transition going from $L_{\rm sph} \propto \sigma^2$ at low luminosities 
to $L_{\rm sph} \propto \sigma^5$ at high luminosities. 
Although the knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
at least three decades  
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995},
it's mainly thanks to large integral-field-spectrograph surveys of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
that our view has been further advanced 
and it's now commonly accepted that most ``elliptical'' galaxies are all but simple and featureless pressure-supported systems. 
More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
In their magnitude-limited survey, systems 
without any signature of disk-like components (neither in the kinematics nor in the photometry) 
dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model embedded disks 
in intermediate-luminosity, early-type galaxies, thus overestimating their $L_{\rm sph}$ 
and mistakenly producing a sharp bent in the $L_{\rm sph} - \sigma$ correlation, rather than a continuously curved relation 
(with $L_{\rm sph} \propto \sigma^{3-4}$ at intermediate luminosities). \\
For the bulges of late-type galaxies we obtained $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$. 
Looking at Figure \ref{fig:mbhmagsph}, one might argue against the statistical significance of this ``tentative'' \emph{late sequence}. 

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario,
and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{late sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans. 
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $= 2.28^{+1.67}_{-1.01}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
More data would be welcome to better constrain the slope of this \emph{late sequence}, 
although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
with the current technological resources. 
In this regard, using data from \cite{jiang2011a}, 
\cite{grahamscott2015} collected a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with virial
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the tentative \emph{late sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated analysis. \\

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type (see legend).
The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
a near-linear relation consistent with a dry-merging formation scenario.
The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
(see Graham et al. 2015, \emph{in preparation}).}
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\acknowledgments
GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes, Gonzalo Diaz and Pablo Rosado for useful discussion. \\
% referee thank you!!
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at {\url https://github.com/rsnemmen/BCES}.
